### 2012-07-18 branches/CUDA/htdocs/porous.tex
creating new CUDA branch from trunk
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1728 40876441-3496-0410-a613-a2fca35b2ae2

>>>>

An example of how to construct a porous media file is provided in
\texttt{util/capillary.c}, which builds an appropriate file for
a square or circular capillary tube. Please see the comments in
the file for further details. Note that the allowed
solid/fluid status values are defined in \texttt{src/site\_map.h}.
A solid boundary is \texttt{BOUNDARY}, while fluid is \texttt{FLUID}.
